Sequence Divergence as the main modulator of structure-sequence correlations

### 2014-11-11 manuscript/cordiv.tex
SAP pdb data added

        To ensure the accuracy of the results obtained from the Spearman correlation matrix of the pdb-level properties, we also apply multivariate linear regression models, with individual sequence-structure correlations as the sole regressand of the models, and the pdb-level properties as the explanatory variables.  Since the number of explanatory variables is comparable to the number of observations (i.e., the number pdb structures in the dataset), we use regularized regression ( reference to R package xx) on the entire dataset of pdb-level properties, and also on the rank transformation of the dataset in order to minimize the effects of potential nonlinearities in data. Depending on value of the free parameter $\alpha$, this generalized regression model is a compromise between {\it ridge regression} -- which attempts to shrink the coefficients of correlated predictors towards each other -- and {\it lasso regression} -- which tends to pick one of the correlated predictors and discard the rest.

        In addition to regularized regression, we have also employed Principal Component Regression on the original dataset and its rank transformation, all of which point to similar set of pdb-level properties as the strongest determinants of sequence-structure correlations.

@@

        \begin{figure}[tbh]
            \centering
            \includegraphics[width=7.2in]{/main_modulators_cormat.pdf} \\
            \caption{{\bf The Spearman correlation matrix of the strongest sequence--structure correlations and the prominent determinants of the strengths of the corresponding relations}. The prefixes {\it r, sd \& mn}}
            \label{fig:mainmods}
        \end{figure}

>>>>

        To ensure the accuracy of the results obtained from the Spearman correlation matrix of the pdb-level properties, we also use multivariate linear regression models, with individual sequence-structure correlations as the sole regressand of the models, and the pdb-level properties as the explanatory variables.  Since the number of explanatory variables is comparable to the number of observations (i.e., the number pdb structures in the dataset), we use regularized regression (reference to R package xx) on the entire dataset of pdb-level properties, and also on the rank transformation of the dataset in order to minimize the effects of potential nonlinearities in data. Depending on value of the free parameter $\alpha$, this generalized regression model is a compromise between {\it ridge regression} -- which attempts to shrink the coefficients of correlated predictors towards each other -- and {\it lasso regression} -- which tends to pick one of the correlated predictors and discard the rest. In addition to regularized regression, we have also employed Principal Component Regression on the original dataset and its rank transformation, all of which point to similar set of pdb-level properties as the strongest determinants of sequence-structure correlations.

@@

        \begin{figure}[tbh]
            \centering
            \includegraphics[width=7.2in]{/main_modulators_cormat.pdf} \\
            \caption{{\bf The Spearman correlation matrix of the strongest sequence--structure correlations and the prominent determinants of the strengths of the corresponding relations}. The variables on the diagonal elements of the matrix from top to bottom represent respectively, the four strongest sequence--structure relations: r4sJC--wcnSC, r4sJC--varea, seqent--wcnSC, seqent--varea, followed by protein properties that modulate the strength of these relations: the correlation between r4sJC--seqent ({\it r.r4sJC.seqent}), variance of r4sJC ({\it var.r4sJC}), variance of sequence entropy ({\it var.seqent}), the variance of hydrogen bond energies ({\it var.hbe}), and the fraction of helical \& $\beta-$sheet secondary structures in the proteins ({\it mean.helix} \& {\it mean.betas} respectively).}
            \label{fig:mainmods}
        \end{figure}
